WritingSSfiles

### 2019-05-22 CreateStockSynthesis.Rmd
Update CreateStockSynthesis file to include age comp writing

```{r setup, include=FALSE}
require(here)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/chris/Documents/GitHub/atlantisom/")
```

@@

>>>>

```{r setup, include=FALSE}
require(here)
require(reshape2)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/chris/Documents/GitHub/atlantisom/")
```

@@

## Writing age composition data

```{r}
#Set effective sample size for age compositions
effN <- 1000
highEffN <- data.frame(species=species, effN=rep(effN, length(species)))

#Sample fish for age composition
age_comp_data <- sample_fish(survey_out, highEffN)
names(age_comp_data) <- c("species","agecl","polygon", "layer","time","numAtAgesamp")

age_comp_data

#Group age composition data by time
require(dplyr)
age_comp_proportion <- age_comp_data %>%
  group_by(time) %>%
  mutate(comp = numAtAgesamp/sum(numAtAgesamp))

#Get the age bins
age_bin_names <- names(sardine.data$agecomp)[10:length(names(sardine.data$agecomp))]
age_bins <- sub("a","",age_bin_names)

#Change data format into flat structure
age_comp_proportion$id <- rep(age_bins,
                              each = nrow(age_comp_proportion)/length(age_bins))

unmelt <- dcast(data = age_comp_proportion,
                formula = time ~agecl,
                value.var = "comp")
age_comp_flat<- cbind(unmelt[order(unmelt$time),],
                      rep(effN,nrow(unmelt)))
names(age_comp_flat)[ncol(age_comp_flat)] <- "nsamp"

## Write age composition data
sardine.data <- SS_write_comps(ss_data_list = sardine.data,
               comp_matrix = list(age_comp_flat[burnin:(burnin+nyears-1),]),
               data_rows = list(sardine.data$styr:(sardine.data$styr+nyears-1)),
               sampling_month = list(rep(7,nyears)),
               data_type = c("agecomp"),
               fleet_number = c(1),
               bins = list(age_bins),
               caal_bool = c(FALSE))
sardine.data$agecomp
